Mbh-n paper

### 2015-11-05 papers/mbhn/mbhn.tex
thu

\subsection{$L_{\rm sph} - n_{\rm sph}$}
Following \cite{graham2001}, 
who showed that the $L_{\rm sph} - n_{\rm sph}$ relation is different for elliptical galaxies and the bulges of disk galaxies (S0+Sp), 
\cite{savorgnan2013} re-analyzed the data from \cite{grahamguzman2003} and \cite{graham2013} 
and obtained two separate $L_{\rm sph} - n_{\rm sph}$ symmetrical linear regressions for elliptical galaxies and the bulges of disk galaxies 
(in the B- and K-band, respectively). 
At the time, the $L_{\rm sph} - n_{\rm sph}$ datasets from \cite{grahamguzman2003} and \cite{graham2013} were of the best quality available 
to investigate the $L_{\rm sph} - n_{\rm sph}$ relation for different galaxy morphological types. 
However, these datasets were not the output of a homogeneous analysis, 
but the collection of the results from various past bulge/disk decomposition studies. 
It is also worth mentioning that, 
although the K-band luminosities of the bulges of disk galaxies had been corrected for internal dust absorption, 
{\bf the dust corrections are not precise today refs??, imagine at the time.....}  
Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram with our top-quality dataset  
derived from our state-of-the-art multicomponent galaxy decompositions, 
that were performed in a consistent manner 
and using the $3.6\rm~\mu m$ band, which is less affected by dust extinction than the K-band. \\
The values of the slope and intercept of the bisector linear regression for the lenticular galaxies 
are not consistent within the errors with those for the spiral galaxies, 
but are consistent within the errors with those for the elliptical galaxies.  
Given this, we conclude that in the $L_{\rm sph} - n_{\rm sph}$ diagram 
elliptical and lenticular galaxies form together a single sequence, 
whereas the combination of lenticular and spiral galaxies do not. 
{\bf why?? dust? multicomponent? classification?}

ell and s0 have same slope -> early seq \\
different from late seq \\

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
\caption{Spheroid absolute magnitude (at $3.6\rm~\mu m$) plotted against spheroid S\'ersic index 
measured along the galaxy major-axis. 
Symbols are coded according to the galaxy morphological type (see legend). 
The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The shallower blue solid line shows the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The inset panel shows the error bars associated to each data point,  
where the error bars have the same color coding as the symbols in the main figure. 
}
\label{fig:magn}
\end{center}
\end{figure}

\subsection{$M_{\rm BH} - n_{\rm sph}$}
in sav13 we had m-l from gs13 for core sersic and sersic \\
however in paper II we say that this is not the case, there are red and blue seq \\
therefore we look for red and blue seq here \\
consistent with each other \\

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
\caption{Black hole mass plotted against spheroid S\'ersic index measured along the galaxy major-axis. 
Symbols are coded according to the galaxy morphological type (see legend). 
The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The shallower blue solid line shows the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The inset panel shows the error bars associated to each data point,  
where the error bars have the same color coding as the symbols in the main figure. 
}
\label{fig:mbhn}
\end{center}
\end{figure}

\section{Discussion}
intr scatter of correlation for all?\\
data suggest that m-n more fundamental than l-n ? \\

@@

 Elliptical (E) (30)	& BCES $(Y|X)$  	     & $8.80 \pm 0.53$ & $-18.16 \pm 53.99$ & $0.76$ & $-$ & $3.02$ \\
 			& mFITEXY $(Y|X)$	     & $8.90 \pm 0.10$ & $4.47 \pm 0.88$ & $0.76$ & $0.29^{+0.14}_{-0.10}$ & $0.56$ \\
 			& {\tt linmix\_err} $(Y|X)$  & $8.84 \pm 0.12$ & $3.56 \pm 1.35$ & $0.76$ & $0.44 \pm 0.12$ & $0.59$ \\ [0.5em]
 			& BCES $(X|Y)$  	     & $8.80 \pm 0.18$ & $8.00 \pm 2.55$ & $0.76$ & $-$ & $1.01$ \\
 			& mFITEXY $(X|Y)$	     & $8.92 \pm 0.15$ & $6.85 \pm 1.75$ & $0.76$ & $0.36^{+0.20}_{-0.15}$ & $0.89$ \\
 			& {\tt linmix\_err} $(X|Y)$  & $8.89 \pm 0.20$ & $6.96 \pm 2.49$ & $0.76$ & $0.63 \pm 0.30$ & $0.89$ \\ [0.5em]
 			& BCES Bisector 	     & $8.80 \pm 0.11$ & $-0.03 \pm 0.10$ & $0.76$ & $-$ & $0.64$ \\
 			& mFITEXY Bisector	     & $8.91 \pm 0.13$ & $5.42 \pm 0.85$ & $0.76$ & $-$ & $0.73$ \\
 			& {\tt linmix\_err} Bisector & $8.85 \pm 0.16$ & $4.73 \pm 1.30$ & $0.76$ & $-$ & $0.67$ \\ [0.5em]

 Lenticular (S0) (11)	& BCES $(Y|X)$  	     & $7.75 \pm 0.58$ & $-11.51 \pm 31.78$ & $0.33$ & $-$ & $2.11$ \\
 			& mFITEXY $(Y|X)$	     & $7.65 \pm 0.12$ & $3.78 \pm 1.20$ & $0.33$ & $0.00^{+0.00}_{-0.00}$ & $0.26$ \\
 			& {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
 			& BCES $(X|Y)$  	     & $7.75 \pm 0.13$ & $3.54 \pm 0.99$ & $0.33$ & $-$ & $0.46$ \\
 			& mFITEXY $(X|Y)$	     & $7.65 \pm 0.12$ & $3.78 \pm 1.20$ & $0.33$ & $0.00^{+0.00}_{-0.00}$ & $0.49$ \\
 			& {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
 			& BCES Bisector 	     & $7.75 \pm 0.13$ & $-0.09 \pm 0.15$ & $0.33$ & $-$ & $0.48$ \\
 			& mFITEXY Bisector	     & $7.65 \pm 0.12$ & $3.78 \pm 0.85$ & $0.33$ & $-$ & $0.49$ \\
 			& {\tt linmix\_err} Bisector & $$ & $$ & $0.33$ & $-$ & $$ \\ [0.5em]

@@

 Early-type (E+S0) (43)	& BCES $(Y|X)$  	     & $8.54 \pm 0.10$ & $4.07 \pm 0.87$ & $0.64$ & $-$ & $0.65$ \\
 			& mFITEXY $(Y|X)$	     & $8.58 \pm 0.07$ & $3.32 \pm 0.34$ & $0.64$ & $0.24^{+0.10}_{-0.07}$ & $0.45$ \\
 			& {\tt linmix\_err} $(Y|X)$  & $8.57 \pm 0.08$ & $3.12 \pm 0.43$ & $0.64$ & $0.32 \pm 0.08$ & $0.53$ \\ [0.5em]
 			& BCES $(X|Y)$  	     & $8.54 \pm 0.09$ & $3.95 \pm 0.55$ & $0.64$ & $-$ & $0.63$ \\
 			& mFITEXY $(X|Y)$	     & $8.59 \pm 0.08$ & $3.88 \pm 0.43$ & $0.64$ & $0.26^{+0.11}_{-0.08}$ & $0.62$ \\
 			& {\tt linmix\_err} $(X|Y)$  & $8.59 \pm 0.09$ & $3.82 \pm 0.50$ & $0.64$ & $0.35 \pm 0.10$ & $0.61$ \\ [0.5em]
 			& BCES Bisector 	     & $8.54 \pm 0.10$ & $4.01 \pm 0.63$ & $0.64$ & $-$ & $0.64$ \\
 			& mFITEXY Bisector	     & $8.59 \pm 0.07$ & $3.58 \pm 0.27$ & $0.64$ & $-$ & $0.58$ \\
 			& {\tt linmix\_err} Bisector & $8.58 \pm 0.08$ & $3.44 \pm 0.33$ & $0.64$ & $-$ & $0.56$ \\ [0.5em]

>>>>

\subsection{$L_{\rm sph} - n_{\rm sph}$}
Following \cite{graham2001}, 
who showed that the $L_{\rm sph} - n_{\rm sph}$ relation is different for elliptical galaxies and the bulges of disk galaxies (S0+Sp), 
\cite{savorgnan2013} re-analyzed the data from \cite{grahamguzman2003} and \cite{graham2013review} 
and obtained two separate $L_{\rm sph} - n_{\rm sph}$ linear regressions for elliptical galaxies and the bulges of disk galaxies 
(in the B- and K-band, respectively). 
At the time, the $L_{\rm sph} - n_{\rm sph}$ datasets from \cite{grahamguzman2003} and \cite{graham2013review} were of the best quality available 
to investigate the $L_{\rm sph} - n_{\rm sph}$ relation for different galaxy morphological types. 
However, these datasets were not obtained from a homogeneous analysis, 
but they were a collection of results taken from various past bulge/disk decomposition studies. 
It is also worth mentioning that, 
although the K-band luminosities of the bulges of disk galaxies had been corrected for internal dust absorption, 
{\bf the dust corrections are not precise today refs??, imagine at the time.....}  
Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram with our high-quality dataset  
derived from state-of-the-art multicomponent galaxy decompositions, 
that were performed in a consistent manner 
and using the $3.6\rm~\mu m$ band, which is less affected by dust extinction than the K-band. \\
\cite{graham2013review} presented a single $L_{\rm sph} - n_{\rm sph}$ correlation for the bulges of disk galaxies (S0+Sp).
However, using our dataset, 
we fit the $L_{\rm sph} - n_{\rm sph}$ relation for elliptical, lenticular and spiral galaxies separately, 
and found that the values of the slope and intercept for the lenticular galaxies 
are not consistent within the errors with those for the spiral galaxies, 
but are consistent within the errors with those for the elliptical galaxies.  
Given this, we conclude that in the $L_{\rm sph} - n_{\rm sph}$ diagram 
elliptical and lenticular galaxies form together a single (\emph{early-type}) sequence, 
whereas the combination of lenticular and spiral galaxies do not. 
{\bf why?? dust? multicomponent? classification?}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
\caption{Spheroid absolute magnitude (at $3.6\rm~\mu m$) plotted against spheroid S\'ersic index 
measured along the galaxy major-axis. 
Symbols are coded according to the galaxy morphological type (see legend).
{\bf crosses outliers!} 
The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The shallower blue solid line shows the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The inset panel shows the error bars associated to each data point,  
where the error bars have the same color coding as the symbols in the main figure. 
}
\label{fig:magn}
\end{center}
\end{figure}

\subsection{$M_{\rm BH} - n_{\rm sph}$}
\cite{grahamscott2013} presented two different $M_{\rm BH} - L_{\rm sph}$ relations for S\'ersic and core-S\'ersic 
spheroids\footnote{Core-S\'ersic spheroids have partially depleted cores relative to their outer S\'ersic light profile, 
whereas S\'ersic spheroids have no central deficit of stars. } \citep{graham2003coresersicmodel,trujillo2004coresersicmodel}.
However, in \emph{Paper II} we found that the slopes of the correlations for S\'ersic and core-S\'ersic spheroids 
are consistent with each other within their $1\sigma$ uncertainties, 
which prevents us from considering them as two separate correlations. 
On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations 
($M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ 
and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$, respectively). \\
Given that early- and late-type galaxies define two separate sequences in both the $L_{\rm sph} - n_{\rm sph}$ 
and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
we investigate substructure in the $M_{\rm BH} - n_{\rm sph}$ diagram. 
Using the results from the modified FITEXY routine, 
we report that 
early-type galaxies follow $M_{\rm BH} \propto n_{\rm sph}^{3.58 \pm 0.27}$, 
while late-type galaxies follow $M_{\rm BH} \propto n_{\rm sph}^{4.55 \pm 0.66}$. 
The Bayesian estimator {\tt linmix\_err} returns consistent results: 
a slope of $3.44 \pm 0.33$ for the early-type galaxies 
and a slope of $4.12 \pm 1.07$ for the late-type galaxies. 
In both cases, the values of the slope and intercept for the early- and late-type galaxies 
are consistent with each other within their $1\sigma$ uncertainties\footnote{In effect, 
considering the results of the modified FITEXY routine, 
the slopes of the relations for early- and late-type galaxies 
are only marginally consistent with each other within their $1\sigma$ uncertainties. 
However, the slopes obtained with Bayesian estimator {\tt linmix\_err} 
are fully consistent with each other within their $1\sigma$ uncertainties. }
Our analysis shows that the early- and late-type galaxies do not define two separate trends in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
i.e.~we do not identify any significant substructure based on the galaxy morphological type. 
The symmetrical linear regression for all galaxies obtained with the modified FITEXY routine is: 
\begin{equation}
\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.18 \pm 0.06) + (3.39 \pm 0.15) \bigl(\log n_{\rm sph} - 0.51 \bigr) .
\end{equation}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
\caption{Black hole mass plotted against spheroid S\'ersic index measured along the galaxy major-axis. 
Symbols are coded according to the galaxy morphological type (see legend). 
{\bf crosses outliers!} 
The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The shallower blue solid line shows the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The linear regressions for early- and late-type galaxies are consistent with each other within their $1\sigma$ uncertainties.  
The inset panel shows the error bars associated to each data point,  
where the error bars have the same color coding as the symbols in the main figure. 
}
\label{fig:mbhn}
\end{center}
\end{figure}

\section{Discussion and conclusions}

intr scatter of correlation for all?\\
data suggest that m-n more fundamental than l-n or m-l woooooh? \\

@@

%Elliptical (E) (30)	& BCES $(Y|X)$  	     & $8.80 \pm 0.53$ & $-18.16 \pm 53.99$ & $0.76$ & $-$ & $3.02$ \\
%			& mFITEXY $(Y|X)$	     & $8.90 \pm 0.10$ & $4.47 \pm 0.88$ & $0.76$ & $0.29^{+0.14}_{-0.10}$ & $0.56$ \\
%			& {\tt linmix\_err} $(Y|X)$  & $8.84 \pm 0.12$ & $3.56 \pm 1.35$ & $0.76$ & $0.44 \pm 0.12$ & $0.59$ \\ [0.5em]
%			& BCES $(X|Y)$  	     & $8.80 \pm 0.18$ & $8.00 \pm 2.55$ & $0.76$ & $-$ & $1.01$ \\
%			& mFITEXY $(X|Y)$	     & $8.92 \pm 0.15$ & $6.85 \pm 1.75$ & $0.76$ & $0.36^{+0.20}_{-0.15}$ & $0.89$ \\
%			& {\tt linmix\_err} $(X|Y)$  & $8.89 \pm 0.20$ & $6.96 \pm 2.49$ & $0.76$ & $0.63 \pm 0.30$ & $0.89$ \\ [0.5em]
%			& BCES Bisector 	     & $8.80 \pm 0.11$ & $-0.03 \pm 0.10$ & $0.76$ & $-$ & $0.64$ \\
%			& mFITEXY Bisector	     & $8.91 \pm 0.13$ & $5.42 \pm 0.85$ & $0.76$ & $-$ & $0.73$ \\
%			& {\tt linmix\_err} Bisector & $8.85 \pm 0.16$ & $4.73 \pm 1.30$ & $0.76$ & $-$ & $0.67$ \\ [0.5em]
%
%Lenticular (S0) (11)	& BCES $(Y|X)$  	     & $7.75 \pm 0.58$ & $-11.51 \pm 31.78$ & $0.33$ & $-$ & $2.11$ \\
%			& mFITEXY $(Y|X)$	     & $7.65 \pm 0.12$ & $3.78 \pm 1.20$ & $0.33$ & $0.00^{+0.00}_{-0.00}$ & $0.26$ \\
%			& {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
%			& BCES $(X|Y)$  	     & $7.75 \pm 0.13$ & $3.54 \pm 0.99$ & $0.33$ & $-$ & $0.46$ \\
%			& mFITEXY $(X|Y)$	     & $7.65 \pm 0.12$ & $3.78 \pm 1.20$ & $0.33$ & $0.00^{+0.00}_{-0.00}$ & $0.49$ \\
%			& {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
%			& BCES Bisector 	     & $7.75 \pm 0.13$ & $-0.09 \pm 0.15$ & $0.33$ & $-$ & $0.48$ \\
%			& mFITEXY Bisector	     & $7.65 \pm 0.12$ & $3.78 \pm 0.85$ & $0.33$ & $-$ & $0.49$ \\
%			& {\tt linmix\_err} Bisector & $$ & $$ & $0.33$ & $-$ & $$ \\ [0.5em]
%
 Early-type (E+S0) (43)	& BCES $(Y|X)$  	     & $8.54 \pm 0.10$ & $4.07 \pm 0.87$ & $0.64$ & $-$ & $0.65$ \\
 			& mFITEXY $(Y|X)$	     & $8.58 \pm 0.07$ & $3.32 \pm 0.34$ & $0.64$ & $0.24^{+0.10}_{-0.07}$ & $0.45$ \\
 			& {\tt linmix\_err} $(Y|X)$  & $8.57 \pm 0.08$ & $3.12 \pm 0.43$ & $0.64$ & $0.32 \pm 0.08$ & $0.53$ \\ [0.5em]
 			& BCES $(X|Y)$  	     & $8.54 \pm 0.09$ & $3.95 \pm 0.55$ & $0.64$ & $-$ & $0.63$ \\
 			& mFITEXY $(X|Y)$	     & $8.59 \pm 0.08$ & $3.88 \pm 0.43$ & $0.64$ & $0.26^{+0.11}_{-0.08}$ & $0.62$ \\
 			& {\tt linmix\_err} $(X|Y)$  & $8.59 \pm 0.09$ & $3.82 \pm 0.50$ & $0.64$ & $0.35 \pm 0.10$ & $0.61$ \\ [0.5em]
 			& BCES Bisector 	     & $8.54 \pm 0.10$ & $4.01 \pm 0.63$ & $0.64$ & $-$ & $0.64$ \\
 			& mFITEXY Bisector	     & $8.59 \pm 0.07$ & $3.58 \pm 0.27$ & $0.64$ & $-$ & $0.58$ \\
 			& {\tt linmix\_err} Bisector & $8.58 \pm 0.08$ & $3.44 \pm 0.33$ & $0.64$ & $-$ & $0.56$ \\ [0.5em]

@@
